quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-08-04 paper-quollr.Rmd
Updated color of data
Updated the limits of the plot

```{r}
clr_choice <- "#bcbddc"

@@

sc_xlims <- c(-0.15, 1.15)
sc_ylims <- c(-0.14, 1.05)

@@

hex_centroids_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = h), 
               fill = "#ffffff")  +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c") +
  interior_annotation("c") +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

wireframe_scurve <- ggplot() +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c") +
  interior_annotation("d") +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

## 2-d vis model
hex_grid_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             size = 0.5, color = clr_choice) +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c")

@@

scurve_umap_model_vis <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from,
                         lineTo = tr_from_to_df_scurve$to,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#33a02c"),
                         enableControls = FALSE,
                         width = "421px", height = "421px")

scurve_umap_model_vis_n <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from,
                         lineTo = tr_from_to_df_scurve$to,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#33a02c"),
                         enableControls = FALSE,
                         width = "300px", height = "300px")

>>>>

```{r}
clr_choice <- "#66B2CC"

@@

sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.25, 1.25)

@@

hex_centroids_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = h), 
               fill = "#ffffff")  +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#FF7755") +
  interior_annotation("c") +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

wireframe_scurve <- ggplot() +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#FF7755") +
  interior_annotation("d") +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

## 2-d vis model
hex_grid_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             size = 0.5, color = clr_choice) +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#FF7755")

@@

scurve_umap_model_vis <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from,
                         lineTo = tr_from_to_df_scurve$to,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#FF7755"),
                         enableControls = FALSE,
                         width = "421px", height = "421px")

scurve_umap_model_vis_n <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from,
                         lineTo = tr_from_to_df_scurve$to,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c(clr_choice, "#FF7755"),
                         enableControls = FALSE,
                         width = "300px", height = "300px")
